Lagrangian Space Nonlinear $E$-mode clustering

### 2016-10-23 ms_disp1/ms_disp1.tex
arxiv version

\addtolength{\hoffset}{-0.525cm}
\addtolength{\textwidth}{1.05cm}
\title{\tcr{Recovery of Primordial Density Field by Reversing the Lagrangian Space Nonlinear $E$-mode clustering}}

\author{Hao-Ran~Yu}%\email{haoran@cita.utoronto.ca}
\affiliation{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing 100871, China}
\affiliation{Canadian Institute for Theoretical Astrophysics, University of Toronto, 60 St. George Street, Toronto, Ontario M5S 3H8, Canada}

\author{Ue-Li~Pen}%\email{pen@cita.utoronto.ca}
\affiliation{Canadian Institute for Theoretical Astrophysics, University of Toronto, 60 St. George Street, Toronto, Ontario M5S 3H8, Canada}
\affiliation{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, 50 St. George Street, Toronto, Ontario M5S 3H4, Canada}
\affiliation{Canadian Institute for Advanced Research, CIFAR Program in Gravitation and Cosmology, Toronto, Ontario M5G 1Z8, Canada}
\affiliation{Perimeter Institute for Theoretical Physics, 31 Caroline Street North, Waterloo, Ontario, N2L 2Y5, Canada}

\author{Hong-Ming Zhu}%email{hmzhu@bao.ac.cn}
\affiliation{Key Laboratory for Computational Astrophysics, National Astronomical Observatories, Chinese Academy of Sciences, 20A Datun Road, Beijing 100012, China}
\affiliation{University of Chinese Academy of Sciences, Beijing 100049, China}

@@

\begin{abstract}
We study the nonlinear $E$-mode clustering in Lagrangian space
by using large scale structure (LSS) $N$-body simulations
and use the displacement field information in Lagrangian space
to recover the primordial linear density field.
We find that, compared to Eulerian nonlinear density fields,
the negative divergence of $E$-mode displacement fields
in Lagrangian space improves the cross-correlation with
initial density field by factor of 6 $\sim$ 7,
containing 2 orders of magnitude more primordial information. 
In reality, the displacement field is dominated by linear evolution
and insensitive of nonlinear shell-crossing, vorticity or
baryonic physics, and thus can be stably solved from only
the final matter distributions.
This illustrates ability of potential density reconstruction algorithms,
to improve the baryonic acoustic oscillation (BAO) mesurements
from current and future large scale structure surveys.

@@

\maketitle
\begin{figure}
 \centering
  \includegraphics[width=0.95\linewidth]{proj.pdf}
  \caption{Visualization of the nonlinear density field $\delta_N$ (top),
  linear density field $\delta_L$ (middle) and the raw recovered density
  field $\delta_R$ (bottom). These projections have 9.375 Mpc$/h$ thickness
  and 400 Mpc$/h$ per side. The top panel shows the nonlinear displacement
  field $\bs\Psi$ by the deformed mesh, which traces the LSS of $\delta_N$.}
  \label{fig.projection}
\end{figure}
\section{Introduction}\label{sec.intro}
Our universe starts from primordial Gaussian perturbations at a very early stage, 
and from those fluctuations, the gravitational instability drives the formation of 
the large scale structure (LSS) distribution of matter
\citep{1970A&A.....5...84Z,1985ApJ...292..371D}.
These structures grow 
linearly until the perturbations are large enough so that the first order 
perturbation theories are unable to analytically describe the LSS distributions 
\citep{2016JCAP...01..043M}. 
As a result, the final nonlinear LSS distribution contains higher order 
statistics, and thus makes it more challenging to be interpreted into basic
cosmological parameters. One such example is that, the baryonic acoustic oscillation (BAO)
scale can be used as a ``standard ruler'' to constrain the cosmic expansion history
and thus probes the dark energy properties \citep{2005NewAR..49..360E}, but
nonlinear evolution smears the BAO features and lowers the measurement
accuracy \citep{2005ApJ...633..560E,2012MNRAS.419.2949N}.
There are various attempts to recover earlier stages
of LSS, in which statistics are closer to Gaussian 
\citep{1992MNRAS.254..315W,2013MNRAS.436..759H}.
Because Gaussian fields can be adequately described by two-point statistics,
ideally after some recovery algorithms, more information can be extracted,
more straightforwardly, by power spectra or two-point correlation functions
\citep{2005MNRAS.360L..82R,2012MNRAS.421..832Y}.

\tcb{Standard BAO reconstruction algorithms apply in Eulerian space.
They usually smooth the nonlinear density field on
linear scale ($\sim$10 Mpc$/h$) and reverse the large 
scale bulk flows by a negative Zel'dovich linear displacement
\citep{2007ApJ...664..675E,2009PhRvD..80l3501N,2009PhRvD..79f3523P}.}
In the linear Lagrangian perturbation theory (LPT), the 
negative divergence of the the displacement field
$-\nabla_q\cdot\bs\Psi(\bs q)$ respect to Lagrangian coordinates $\bs q$
gives the linear density field \citep{2010PhDT.........4J},
\tcr{and in many literatures
\cite{2013MNRAS.428..141N,2014PhRvD..89h3515C,2016JCAP...03..017B}
$\nabla_q\cdot\bs\Psi(\bs q)$ is compared with various standard LPT
and corrected LPT initial conditions. Their motivation was
trying to correct or modify the LPT displacement fields
in order that the final positions of particles are brought
closer to $N$-body results. Their results show that 
all LPT methods are still unable to mimic the shell-crossing
scales given by $N$-body simulation. Because of the absence
of Lagrangian space information in observations, few density
reconstruction algorithms are developed according to the relation
between displacement and linear density. However,
there are techniques to estimate the displacement field from a final 
distribution of matter.}
For example, when a homogeneous initial matter distribution 
is assumed, there is a unique solution of curl-less displacement field to relate 
the initial and final distributions without shell-crossing. This solution can be 
solved by a metric transformation equation
\citep{1995ApJS..100..269P,1998ApJS..115...19P}.
In 1-dimensional (1D) case, the exact solution 
simplifies to an ordering of matter elements by Eulerian coordinates.
Zhu {\it et al.} \cite{2016arXiv160907041Z} apply this algorithm to the result
of an 1D simulation \citep{2016JCAP...01..043M} and obtain an estimated
displacement field $\tilde\Psi(q)$, and find
that this new method well recovers the linear
information and reconstructs 1D BAO peak in correlation function.
\tcr{In 3D and more realistic cases, one needs to
carefully consider effects of curl, shell-crossing, 
complicated baryonic physics and biased tracers (galaxies).}

\tcr{Before these steps, we need to quantify the amount of linear information
that can be recovered\footnote{To avoid ambiguity, we call
$\delta_R=-\nabla_q\cdot\bs\Psi(\bs q)$ recovered linear density field, which
requires $\bs\Psi(\bs q)$ from $N$-body simulations, while
$-\nabla_q\cdot\tilde{\bs \Psi}(\bs q)$ is called the
reconstructed density field.}
 from the full nonlinear displacement field $\bs\Psi(\bs q)$.
In $\bs\Psi(\bs q)$ from $N$-body simulations,
(1) shell-crossing effects are fully considered; (2) $E$-mode displacement
field is used for recovering the linear information (although $B$-mode is
also present); (3) the setup is clean in absence of baryons and realistic
observables. So it sets the best quality that potential reconstruction
algorithms can achieve and further reconstructions by $\tilde{\bs \Psi}(\bs q)$
can be compared with this result. Actually, in the later discussions and
our next works we will show that, compared to $\tilde{\bs \Psi}(\bs q)$,
additional information (shell-crossing) do not enhance the reconstruction
prominently. Further more, we study the scale dependent cross-correlation
between $-\nabla_q\cdot\bs\Psi(\bs q)$ and linear density field
and construct optimal Wiener filters to get the optimal filtered
recovered linear density field and recovered linear power spectrum.}

@@

\begin{figure}[t] \centering
  \includegraphics[width=1.0\linewidth]{power.pdf}
  \caption{\tcr{Power spectra of $\delta_L$, $\delta_N$, and the decomposition
  of $P_{LL}$ into correlated parts and noise terms according to equation
  (\ref{eq.power}).}}
  \label{fig.recopower}
\end{figure}

To quantify the linear information in the recovered density field, we decompose $\delta_L$ in Fourier space as
\begin{equation}\label{eq.decompose}
    \delta_L(k)=r'\delta_R+\delta_n,
\end{equation}
where $r'\delta_R$ is completely correlated with linear density $\delta_L$. Correlating equation (\ref{eq.decompose}) with $\delta_R$ gives
\begin{equation}
    P_{LR}=r'P_{RR}+P_{nR},
\end{equation}
where $P_{ij}\equiv\langle\delta_i\delta_j\rangle$ denotes the cross power 
spectrum. Since $\delta_n$ is uncorrelated with $\delta_R$, $P_{nR}=0$. With the 
definition of cross correlation coefficient $r(\delta_L,\delta_R)\equiv P_{LR}/\sqrt{P_{LL}P_{RR}}$ 
and bias $b^2=P_{RR}/P_{LL}$, we solve $r'=P_{LR}/P_{RR}=rb^{-1}$.
Note that these computations above and below can also be applied on $\delta_N$ for
comparison, by replacing ``$_R$'' with ``$_N$'' in the equations,
while we do not rewrite them explicitly
in the paper for simplicity. From these, we plot the cross 
correlation coefficient $r_{LN}=r(\delta_L,\delta_N)$ and
$r_{LR}=r(\delta_L,\delta_R)$ in Fig.\ref{fig.corr}. Clearly, $
\delta_R$ contains much more linear information on smaller scales.

@@

@@

To further illustrate the improvement in real space
one point function correlations,
in Fig.\ref{fig.pdfs} we use the probability distribution
as functions (PDFs) of $(\delta_L,\delta_N)$ and $(\delta_L,\delta_R)$
to show the point-point correlation between these two pairs of density
fields. Since $\delta_n$ in equation (\ref{eq.decompose}) is
uncorrelated, we use Wiener filtered fields. To keep the
consistency over $\delta_L$, $\delta_N$ and $\delta_R$, we
use the $W(k)=r^2_{LR}$ as the Wiener filter.
The grey-scaled plots in the center of both panels show the 2-variable PDFs,
whereas their projections onto each variable are just
1-variable PDFs -- $f(\delta_L)$, $f(\delta_N)$ and $f(\delta_R)$, shown
as red/blue curves on the axes of Fig.\ref{fig.pdfs}.
In the top panel, $\delta_N$ shows an approximate log-normal
distribution (blue curve) and $\delta_L$ follows an expected
Gaussian distribution. They show tiny positive correlation in the
2D PDF.
Because in Fourier space, $\delta_L$ and $\delta_N$ have
correlations on only very large, linear scales (Fig.\ref{fig.corr}),
they result in little correlation in real space -- initial density fluctuations
in Lagrangian coordinates are evolved/transformed to Eulerian coordinates.
As the recovery is done in Lagrangian space, it recovers
certain amount of correlation, as shown in the 2D PDF of the bottom panel
of Fig.\ref{fig.pdfs}. One can also see that $\delta_R$ follows
a much closer Gaussian distribution (blue curve of the bottom panel).
In denser regions of $\delta_L$, $\delta_R$ is saturated at
$\delta_R=3$, signifying the extreme collapsing of matter \citep{2013MNRAS.428..141N}:
$\delta_R=-\nabla\cdot\bs\Psi=\nabla\cdot\bs q=3$. Shell crossing
makes $\delta_R$ oscillate around 3. These second uncorrelated peaks
damp out as we go to higher redshifts. \tcr{more?}

@@

\tcr{The advantage of using displacement field in reconstruction is
its insensitive response from highly nonlinearities --
densest regions form because matter elements, after shell crossing,
stop experiencing the linear extrapolated of Zel'dovich approximation.
i.e. the displacement fields are dominated by early stage linear processes,
which is the Lagrangian-Eulerian coordinate transform,
while late stage shell-crossing, nonlinear and baryonic processes
only fine-tunes the final position $\bs x$
\citep{2014PhRvD..89h3515C}. Compared with estimated displacement fields $\tilde{\bs \Psi}(\bs q)$
by \cite{1995ApJS..100..269P}, which do not have shell crossing,
the additional shell-crossing information in $\bs\Psi(\bs q)$
is uncorrelated with $\delta_L$. This insensitive response from
nonlinearities enables the stability of reconstruction algorithms,
which are expected to give similar results of this paper. 
In contrast, traditional
treatments in reconstruction deals directly on density fields which sensitively
relies on nonlinear processes --  density values can vary by orders
of magnitude due to nonlinear/baryonic physics and many sources of errors.}

\section*{Acknowledgements}
We thank Pengjie Zhang for helpful discussions which triggered
the inspiration of the work.
HRY acknowledges General Financial Grant No.2015M570884 and Special Financial Grant No.2016T90009 from the China Postdoctoal Science Foundation.
HMZ acknowledges the support of the Chinese MoST 863 program under Grant
No. 2012AA121701, the CAS Science Strategic Priority Research Program
XDB09000000 and the NSFC under Grant No. 11373030.
The Dunlap Institute is funded through an endowment established by the David Dunlap family and the University of Toronto.
Research at the Perimeter Institute is supported by the Government of Canada
through Industry Canada and by the Province of Ontario through the Ministry of
Research $\&$ Innovation.

>>>>

\addtolength{\hoffset}{-0.525cm}
\addtolength{\textwidth}{1.05cm}
\title{Lagrangian Space Nonlinear $E$-mode clustering}

\author{Hao-Ran~Yu}\email{haoran@cita.utoronto.ca}
\affiliation{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing 100871, China}
\affiliation{Canadian Institute for Theoretical Astrophysics, University of Toronto, 60 St. George Street, Toronto, Ontario M5S 3H8, Canada}

\author{Ue-Li~Pen}\email{pen@cita.utoronto.ca}
\affiliation{Canadian Institute for Theoretical Astrophysics, University of Toronto, 60 St. George Street, Toronto, Ontario M5S 3H8, Canada}
\affiliation{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, 50 St. George Street, Toronto, Ontario M5S 3H4, Canada}
\affiliation{Canadian Institute for Advanced Research, CIFAR Program in Gravitation and Cosmology, Toronto, Ontario M5G 1Z8, Canada}
\affiliation{Perimeter Institute for Theoretical Physics, 31 Caroline Street North, Waterloo, Ontario, N2L 2Y5, Canada}

\author{Hong-Ming Zhu}\email{hmzhu@bao.ac.cn}
\affiliation{Key Laboratory for Computational Astrophysics, National Astronomical Observatories, Chinese Academy of Sciences, 20A Datun Road, Beijing 100012, China}
\affiliation{University of Chinese Academy of Sciences, Beijing 100049, China}

@@

\begin{abstract}
We study the nonlinear $E$-mode clustering in Lagrangian space
by using large scale structure (LSS) $N$-body simulations
and use the displacement field information in Lagrangian space
to recover the primordial linear density field.
We find that, compared to Eulerian nonlinear density fields,
the $E$-mode displacement fields
in Lagrangian space improves the cross-correlation scale $k$ with
initial density field by factor of 6 $\sim$ 7,
containing 2 orders of magnitude more primordial information.
This illustrates ability of potential density reconstruction algorithms,
to improve the baryonic acoustic oscillation (BAO) mesurements
from current and future large scale structure surveys.

@@

\maketitle

\section{Introduction}\label{sec.intro}
Our universe starts from primordial Gaussian perturbations at a very early stage, 
and from those fluctuations, the gravitational instability drives the formation of 
the large scale structure (LSS) distribution of matter
\citep{1970A&A.....5...84Z,1985ApJ...292..371D}.
These structures grow 
linearly until the perturbations are large enough so that the first order 
perturbation theories are unable to analytically describe the LSS distributions 
\citep{2016JCAP...01..043M}. 
As a result, the final nonlinear LSS distribution contains higher order 
statistics, and thus makes it more challenging to be interpreted into basic
cosmological parameters. One such example is that, the baryonic acoustic oscillation (BAO)
scale can be used as a ``standard ruler'' to constrain the cosmic expansion history
and thus probes the dark energy properties \citep{2005NewAR..49..360E}, but
nonlinear evolution smears the BAO features and lowers the measurement
accuracy \citep{2005ApJ...633..560E,2012MNRAS.419.2949N}.
There are various attempts to recover earlier stages
of LSS, in which statistics are closer to Gaussian 
\citep{1992MNRAS.254..315W,2013MNRAS.436..759H}.
Because Gaussian fields can be adequately described by two-point statistics,
ideally after some recovery algorithms, more information can be extracted,
more straightforwardly, by power spectra or two-point correlation functions
\citep{2005MNRAS.360L..82R,2012MNRAS.421..832Y}.

Standard BAO reconstruction algorithms apply in Eulerian space.
They usually smooth the nonlinear density field on
linear scale ($\sim$10 Mpc$/h$) and reverse the large 
scale bulk flows by a negative Zel'dovich linear displacement
\citep{2007ApJ...664..675E,2009PhRvD..80l3501N,2009PhRvD..79f3523P}.
In the linear Lagrangian perturbation theory (LPT), the 
negative divergence of the the displacement field
$-\nabla_q\cdot\bs\Psi(\bs q)$ respect to Lagrangian coordinates $\bs q$
gives the linear density field \citep{2010PhDT.........4J},
and in many literatures
\cite{2013MNRAS.428..141N,2014PhRvD..89h3515C,2016JCAP...03..017B}
$\nabla_q\cdot\bs\Psi(\bs q)$ is compared with various standard LPT
and corrected LPT initial conditions. Their motivation was
trying to correct or modify the LPT displacement fields
in order that the final positions of particles are brought
closer to $N$-body results. Because of the absence
of Lagrangian space information in observations, few density
reconstruction algorithms are developed according to the relation
between displacement and linear density. However,
there are techniques to estimate the displacement field from a final 
distribution of matter.
For example, when a homogeneous initial matter distribution 
is assumed, there is a unique solution of curl-less displacement field to relate 
the initial and final distributions without shell-crossing. This solution can be 
solved by a metric transformation equation
\citep{1995ApJS..100..269P,1998ApJS..115...19P}.
In 1-dimensional (1D) case, the exact solution 
simplifies to an ordering of matter elements by Eulerian coordinates.
Zhu {\it et al.} \cite{2016arXiv160907041Z} apply this algorithm to the result
of an 1D simulation \citep{2016JCAP...01..043M} and obtain an estimated
displacement field $\tilde\Psi(q)$, and find
that this new method well recovers the linear
information and reconstructs 1D BAO peak in correlation function.
In 3D and more realistic cases, one needs to
carefully consider effects of curl, shell-crossing, 
complicated baryonic physics and biased tracers (galaxies).

\begin{figure}
 \centering
  \includegraphics[width=0.95\linewidth]{proj.pdf}
  \caption{Visualization of the nonlinear density field $\delta_N$ (top),
  linear density field $\delta_L$ (middle) and the raw recovered density
  field $\delta_R$ (bottom). These projections have 9.375 Mpc$/h$ thickness
  and 400 Mpc$/h$ per side. The top panel shows the nonlinear displacement
  field $\bs\Psi$ by the deformed mesh, which traces the LSS of $\delta_N$.}
  \label{fig.projection}
\end{figure}

Before these steps, we need to quantify the amount of linear information
that can be recovered\footnote{To avoid ambiguity, we call
$\delta_R\equiv-\nabla_q\cdot\bs\Psi(\bs q)$ recovered linear density field, which
requires $\bs\Psi(\bs q)$ from $N$-body simulations, while
$-\nabla_q\cdot\tilde{\bs \Psi}(\bs q)$ is called the
reconstructed density field, which uses the estimated displacement field.}
 from the full nonlinear displacement field $\bs\Psi(\bs q)$.
In $\bs\Psi(\bs q)$ from $N$-body simulations,
(1) shell-crossing effects are fully considered; (2) $E$-mode displacement
field is used for recovering the linear information (although $B$-mode is
also present); (3) the setup is clean in absence of baryons and realistic
observables. Further reconstructions by $\tilde{\bs \Psi}(\bs q)$
can be compared with this result.
Further more, we study the scale dependent cross-correlation
between $-\nabla_q\cdot\bs\Psi(\bs q)$ and linear density field
and construct optimal Wiener filters to get the optimal filtered
recovered linear density field and recovered linear power spectrum.

@@

To quantify the linear information in the recovered density field, we decompose $\delta_L$ in Fourier space as
\begin{equation}\label{eq.decompose}
    \delta_L(k)=r'\delta_R+\delta_n,
\end{equation}
where $r'\delta_R$ is completely correlated with linear density $\delta_L$. Correlating equation (\ref{eq.decompose}) with $\delta_R$ gives
\begin{equation}
    P_{LR}=r'P_{RR}+P_{nR},
\end{equation}
where $P_{ij}\equiv\langle\delta_i\delta_j\rangle$ denotes the cross power 
spectrum. Since $\delta_n$ is uncorrelated with $\delta_R$, $P_{nR}=0$. With the 
definition of cross correlation coefficient $r(\delta_L,\delta_R)\equiv P_{LR}/\sqrt{P_{LL}P_{RR}}$ 
and bias $b^2=P_{RR}/P_{LL}$, we solve $r'=P_{LR}/P_{RR}=rb^{-1}$.
Note that these computations above and below can also be applied on $\delta_N$ for
comparison, by replacing ``$_R$'' with ``$_N$'' in the equations,
while we do not rewrite them explicitly
in the paper for simplicity. From these, we plot the cross 
correlation coefficient $r_{LN}=r(\delta_L,\delta_N)$ and
$r_{LR}=r(\delta_L,\delta_R)$ in Fig.\ref{fig.corr}.
$r_{LN}$ shows no correlation starting from $k\simeq 0.4 h/$Mpc \citep{2004MNRAS.355..129S}.
Clearly, $
\delta_R$ contains much more linear information on smaller scales.

@@

\begin{figure}[t] \centering
  \includegraphics[width=1.0\linewidth]{power.pdf}
  \caption{Power spectra of $\delta_L$, $\delta_N$, and the decomposition
  of $P_{LL}$ into correlated parts and noise terms according to equation
  (\ref{eq.power}).}
  \label{fig.recopower}
\end{figure}

@@

To further illustrate the improvement in real space
one point function correlations,
in Fig.\ref{fig.pdfs} we use the probability distribution
as functions (PDFs) of $(\delta_L,\delta_N)$ and $(\delta_L,\delta_R)$
to show the point-point correlation between these two pairs of density
fields. Since $\delta_n$ in equation (\ref{eq.decompose}) is
uncorrelated, we use Wiener filtered fields. To keep the
consistency over $\delta_L$, $\delta_N$ and $\delta_R$, we
use the $W(k)=r^2_{LR}$ as the Wiener filter.
The grey-scaled plots in the center of both panels show the 2-variable PDFs,
whereas their projections onto each variable are just
1-variable PDFs -- $f(\delta_L)$, $f(\delta_N)$ and $f(\delta_R)$, shown
as red/blue curves on the axes of Fig.\ref{fig.pdfs}.
In the top panel, $\delta_N$ shows an approximate log-normal
distribution (blue curve) and $\delta_L$ follows an expected
Gaussian distribution. They show tiny positive correlation in the
2D PDF.
Because in Fourier space, $\delta_L$ and $\delta_N$ have
correlations on only very large, linear scales (Fig.\ref{fig.corr}),
they result in little correlation in real space -- initial density fluctuations
in Lagrangian coordinates are evolved/transformed to Eulerian coordinates.
As the recovery is done in Lagrangian space, it recovers
certain amount of correlation, as shown in the 2D PDF of the bottom panel
of Fig.\ref{fig.pdfs}. One can also see that $\delta_R$ follows
a much closer Gaussian distribution (blue curve of the bottom panel).
In denser regions of $\delta_L$, $\delta_R$ is saturated at
$\delta_R=3$, signifying the extreme collapsing of matter \citep{2013MNRAS.428..141N}:
$\delta_R=-\nabla\cdot\bs\Psi=\nabla\cdot\bs q=3$. Shell crossing
makes $\delta_R$ oscillate around 3. These second uncorrelated peaks
damp out as we go to higher redshifts.

@@

The advantage of using displacement field in reconstruction is
its insensitive response from highly nonlinearities.
nonlinear densities $\delta_N$ can be arbitrarily large -- 
one expect virialized regions to be observable, where nonlinear
density is given by the inverse determinant of the Jacobian
$\delta_N=|\bs J|^{-1}\gtrsim 200$.
However, reconstructed densities $\delta_R$ is given by
the trace $\rm{tr}(\bs J)$ and saturates at 3.
Actually, the displacement fields are dominated by early stage linear processes,
which is the Lagrangian-Eulerian coordinate transform,
while late stage shell-crossing, nonlinear and baryonic processes
only fine-tunes the final position $\bs x$
\citep{2014PhRvD..89h3515C}. Compared with estimated displacement fields $\tilde{\bs \Psi}(\bs q)$
by \cite{1995ApJS..100..269P}, which do not have shell crossing,
the additional shell-crossing information in $\bs\Psi(\bs q)$
is uncorrelated with $\delta_L$. This insensitive response from
nonlinearities enables the stability of reconstruction algorithms,
which are expected to give similar results of this paper. 
In contrast, traditional
treatments in reconstruction deals directly on density fields which sensitively
relies on nonlinear processes --  density values can vary by orders
of magnitude due to nonlinear/baryonic physics and many sources of errors.

\section*{Acknowledgements}
We thank Pengjie Zhang for helpful discussions and comments.
We acknowledge funding from NSERC.
HRY acknowledges General Financial Grant No.2015M570884 and Special Financial Grant No.2016T90009 from the China Postdoctoal Science Foundation.
HMZ acknowledges the support of the Chinese MoST 863 program under Grant
No. 2012AA121701, the CAS Science Strategic Priority Research Program
XDB09000000 and the NSFC under Grant No. 11373030.
Research at the Perimeter Institute is supported by the Government of Canada
through Industry Canada and by the Province of Ontario through the Ministry of
Research $\&$ Innovation.
